\cvsection{Certifications}
\begin{cventries}
  \cventry
    {Coursera | University of Pennsylvania}
    {\href{https://drive.google.com/open?id=0B0SiIiwo-oPobkU3UDlBY3RXVTQ}{Robotics Specialization}}
    {}
    {Jun. 2017 - Present}
    {
      \begin{cvitems}
        \item {Pursuing Robotics Specialization coursework from coursera. Already completed 5 out of 6 courses.}
        \item {Completed courses on \href{https://www.coursera.org/account/accomplishments/certificate/QS5GBKTUNU2G}{Aerial Robotics},  \href{https://www.coursera.org/account/accomplishments/certificate/MQZ2DBARND8Y}{Robotics: Computational Motion Planning}, \href{https://www.coursera.org/account/accomplishments/verify/CDK6J2QNMV7Y}{Robotics: Mobility},   \href{https://www.coursera.org/account/accomplishments/verify/MY9843D7KFDY}{Robotics: Perception} and  \href{https://www.coursera.org/account/accomplishments/verify/UBPR6FJU9Q47}{Robotics: Estimation and Learning}}
        \item {Working on Capstone project on Autonomous Robot Track which is a major project required to complete the specialization. It includes simulation, Path Planning, Sensor calibration, Designing of control algorithms and Extended Kalman filter to navigate autonomously through designed environment}
        \item {Learned various aspects of Designing, Simulations and controls technique of Robotics. Completed all the verified assignments on Octave, Python and ROS as part of the course.}
      \end{cvitems}
}      

 \cventry
    {Coursera | Stanford University}
    { \href{https://www.coursera.org/account/accomplishments/certificate/9SSNE58D35EH}{Machine Learning}}
    {}
    {August 2017}
    {
      \begin{cvitems}
        \item {Successfully completed course on Machine Learning by Prof. Andrew Ng, Stanford University.}
        \item {Learned various algorithms for the foundation of Machine Learning and implemented on octave.}
        \item {Completed a Rudimentary Spam Classifier and handwritten digit recogniser Project as a part of Machine Learning Course.}\\
      \end{cvitems}
}
\cventry
    {Coursera | deeplearning.ai}
    { \href{https://drive.google.com/open?id=0B0SiIiwo-oPoOEhTenpjRGpiNUE}{Deep Learning Specialization}}
    {}
    {October 2017-Present}
    {
      \begin{cvitems}
        \item {Successfully completed  first course \href{https://www.coursera.org/account/accomplishments/certificate/RWG9PBQF5MK9}{Neural Networks and Deep Learning} of Deep Learning Specialization by Dr. Andrew Ng}
      \end{cvitems}
}
\end{cventries}